pediatricResults

### 2021-10-28 metanalysis_visualization/pedsResults.Rmd
adding trends meta-analysis

>>>>

#### Meta-analysis of temporal trends

```{r}
# Fixed effect

load("output/peds_psy_aggResults_BCH.RData")
df_meta <- bootstrapped_fitted_df %>%
  filter(iteration %in% 1:4) %>%
  mutate(siteid = as.factor(iteration))

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
theme_plots <- theme_bw() +
  theme(strip.text = element_text(size = 5),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 6),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 10),
        plot.subtitle = element_text(size = 9, face = "italic"))
theme_set(theme_plots)

# Colorblind palette
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

## Fixed Effect model

fixed_model <- lm(
  percentage ~ time*period + time*siteid,
  data = df_meta)

result_fixed_model <- broom::tidy(fixed_model)

df_meta$fitted_fixed <- fitted(fixed_model)

pvalue <- result_fixed_model[result_fixed_model$term == "time:periodduring_pandemic",
                             "p.value"][[1]] %>%
  round(4)

annotation_plot <- paste0(
  "Difference of trend before/during pandemic: p",
  ifelse(pvalue == 0,
         "< 1e^-4",
         paste0("=", as.character(pvalue)))
)

ggplot(data = df_meta, aes(x = time_p,
                           y = percentage,
                           color = siteid)) +
  geom_point() +
  geom_line(aes(y=fitted_fixed), data = df_meta[df_meta$period == "before_pandemic", ]) +
  geom_line(aes(y=fitted_fixed), data = df_meta[df_meta$period == "during_pandemic", ]) +
  geom_line(aes(y=predicted, color=NULL), data = df_meta[df_meta$period == "before_pandemic", ]) +
  geom_line(aes(y=predicted, color=NULL), data = df_meta[df_meta$period == "during_pandemic", ]) +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  labs(title = "Meta-analysis: percentage of visits with Mental Health ICD code across sites",
       subtitle = "Sites effect treated as fixed effect",
       color = "Sites",
       x = "Calendar date",
       y = "Percentage"
       ) +
  annotate("text",
           x = as.Date("2019-10-01"),
           y = max(df_meta[["percentage"]]),
           label = annotation_plot,
           )

# Same but with random effect for the sites effect on trends
library(lme4)
mixed_model <- lmer(percentage ~ time*period + (time|siteid),
                    data = df_meta)
